Active Object Search with a Mobile Device for the Visually Impaired

### 2018-11-22 paper.tex
Edit figure, edit to way work was referened in sec2

Another approach is to discard tags completely and rely on computer vision to perform the object detection, something that has become more plausible with recent improvements to feature detectors and deep networks~\cite{huang2017speed,redmon2016you}. The system described~\cite{schauerte2012assistive} uses a combination of SIFT and SURF to detect known objects when they are in the camera's view and guide the user to them using sonified guidance instructions. This system is more flexible than the tag-based ones, but have the same drawback of being passive and rely on chance for the user to place the object within the camera's view in the first place. The paper also does not report on any performance metrics. In~\cite{bigham2010vizwiz}, the authors discuss their VizWiz system that offloads the object recognition tasks to an Amazon Mechanical Turk worker that then provides feedback on where the object of interest is located relative to the user. The VizWiz has the advantage of being fairly robust and is able to classify a great deal of objects with little effort from the user and can provide natural, human-generated and curated directions. However, this approach does not address the issue of enhancing user independence, since the user is now beholden to an online worker instead of a relative, friend or bystander. Furthermore, a good internet connection is required on the device, perhaps limiting use in some poor-reception areas.

@@

In~\cite{caicedo2015active,gonzalez2015active}, the authors implemented an active search strategy for classifying objects within cluttered images. Their approaches use different methods, but both involve using a model to generate windows of interest to submit to a classifier for classification. The size and locations of the windows within the image are generated using the spatial relationship between objects, taken from the SUNCG and PASCAL datasets, and are iteratively changed based on the output from the respective models. The advantage of their approaches over their contemporaries is that far fewer windows are generated and submitted to the classifier, resulting in lower object classification times. They also report comparable accuracy when compared to their contemporaries.

Similarly, roboticists have moved to incorporate similar strategies on robotic platforms to improve autonomous object search, manipulation and localisation tasks. The authors in~\cite{dogar2014object} developed a planning algorithm that allows a robotic manipulator to select an object to move that optimally executes an object search or exploration task in a cluttered environment. In~\cite{aydemir2011search}, the authors implemented an MDP that generates the optimal search strategy to find an object in a room over a belief state of object positions and configurations. However, the authors trained their MDP using a custom object-placement and configuration probabilities and have shown that the results are sensitive to changes within this distribution.

@@

The model is trained until it converges to the optimal policy, or for a total of approximately 17 million episodes. The parameter, $\alpha$, that controls the exploration vs.\ exploitation behaviour during training maximises exploration when it is set to $1.0$ and exploitation when it is $0.0$. We set $\alpha$ to a function that starts at a high exploration value and exponentially changes it behaviour to exploitation as it becomes more trained. $\alpha$ is given by

\begin{equation}
  \alpha = \exp\Big(\frac{-i}{10n_{states}}\Big) - 0.001,
\end{equation}
where $i$ is the episode index.  $\gamma$ is set to 0.95 to prioritise long-term reward.

@@

The app was developed on and experimented with an Asus ZenPhone AR\footnote{asus.com/uk/Phone/ZenFone-AR-ZS571KL/} running Android version 7.0 with the ARCore\footnote{https://developers.google.com/ar/} SDK enabled. No hardware or software modifications were required.

@@

\noindent The TAR is a measure of how successful the system was at directing a participant to the target object within the 15-step limit we set and is simply calculated as a proportion of the number completed searches vs.\ the total number of searches. Please note, however, that this plot is dependant on the step-limit we selected and should not be taken as an absolute measure of performance, but is rather presented to provide context to the other results we present. Figure~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off at higher step-limits. \uline{The angled tail at the 15-step limit is interesting to note, however. WHY}

@@

\uline{COMPARE RESULTS FROM ROBOTS? APPROX 100s FOR PLANNING AND EXECUTION}

@@

% \clearpage
\bibliographystyle{apalike}
\bibliography{bib}

>>>>

Another approach is to discard tags completely and rely on computer vision to perform the object detection, something that has become more plausible with recent improvements to feature detectors and deep networks~\cite{huang2017speed,redmon2016you}. SIFT and SURF-based object detectors have also been used to detect known objects when they are in the camera's view and guide the user to them using sonified guidance instructions~\cite{schauerte2012assistive}. This system is more flexible than the tag-based ones, but have the same drawback of being passive and rely on chance for the user to place the object within the camera's view in the first place. The paper also does not report on any performance metrics. The VizWize system~\cite{bigham2010vizwiz} offloads the object recognition tasks to an Amazon Mechanical Turk worker that then provides feedback on where the object of interest is located relative to the user. The VizWiz has the advantage of being fairly robust and is able to classify a great deal of objects with little effort from the user and can provide natural, human-generated and curated directions. However, this approach does not address the issue of enhancing user independence, since the user is now beholden to an online worker instead of a relative, friend or bystander. Furthermore, a good internet connection is required on the device, perhaps limiting use in some poor-reception areas.

@@

Two research teams have recently implemented an active object search strategy into their image classifiers~\cite{caicedo2015active,gonzalez2015active}. Their approaches use different methods, but both involve using a model to generate windows of interest to submit to a classifier for classification. The size and locations of the windows within the image are generated using the spatial relationship between objects, taken from the SUNCG and PASCAL datasets, and are iteratively changed based on the output from the respective models. The advantage of their approaches over their contemporaries is that far fewer windows are generated and submitted to the classifier, resulting in lower object classification times. They also report comparable accuracy compared to their counterparts.

Similarly, roboticists have moved to incorporate similar strategies on robotic platforms to improve autonomous object search, manipulation and localisation tasks. Researchers have developed a planning algorithm that allows a robotic manipulator to select an object to move that optimally executes an object search or exploration task in a cluttered environment~\cite{dogar2014object}. Another team implemented an MDP that generates the optimal search strategy to find an object in a room over a belief state of object positions and configurations~\cite{aydemir2011search}. However, the authors trained their MDP using a custom object-placement and configuration probabilities and have shown that the results are sensitive to changes within this distribution.

@@

The model is trained until it converges to the optimal policy, or for a total of approximately 17 million episodes. The parameter, $\alpha$, that controls the exploration vs.\ exploitation behaviour during training maximises exploration when it is set to $1$ and exploitation when it is $0$. We set $\alpha$ to a function that starts at a high exploration value and exponentially changes it behaviour to exploitation as it becomes more trained. $\alpha$ is given by

\begin{equation}
  \alpha = \exp\Big(\frac{-i}{10s_{total}}\Big) - 0.001,
\end{equation}
where $i$ is the episode index.  $\gamma$ is set to 0.95 to prioritise long-term reward.

@@

The app was developed on and experimented with an Asus ZenPhone AR\todo{No footers}\footnote{asus.com/uk/Phone/ZenFone-AR-ZS571KL/} running Android version 7.0 with the ARCore\footnote{https://developers.google.com/ar/} SDK enabled. No hardware or software modifications were required.

@@

\noindent The TAR is a measure of how successful the system was at directing a participant to the target object within the 15-step limit we set and is simply calculated as a proportion of the number completed searches vs.\ the total number of searches. Please note, however, that this plot is dependant on the step-limit we selected and should not be taken as an absolute measure of performance, but is rather presented to provide context to the other results we present. Figure~\ref{fig:tar-steps} shows the TAR as a function of the step-limit and it shows that there is a gradual increase in the TAR as the step limit increases, but tapers off at higher step-limits. The angled tail at the 15-step limit is interesting to note, however. \todo{WHY}

@@

\todo{COMPARE RESULTS FROM ROBOTS? APPROX 100s FOR PLANNING AND EXECUTION}

@@

% \clearpage
\bibliographystyle{apalike}
{\small
\bibliography{bib}}
